Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network

### 2013-09-05 doc/paper.tex
finished final edits

Within the next few years, the first generation of gravitational-wave
interferometers capable of regularly detecting astrophysical sources will
come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Advanced Virgo
detectors (and the anticipated LIGO India detector)
 will provide the first insights into the final moments of
binary compact object mergers, including the mergers of binary neutron
star systems.  Intense preparations are underway to characterize and
extract as much physical information as possible from these signals.

@@

By employing the full parameter-estimation machinery that will
eventually be used in the Advanced LIGO/Virgo era, our results
 give realistic estimates of the capabilities of
advanced ground-based detectors to characterize BNS systems.  Until
recently, the majority of studies have employed the Fisher-matrix
formalism which was first adapted for gravitational-wave parameter
estimation by \citet{FinnDetection}.  While each of these studies
\citep{PoissonWill,CutlerFlanagan,ArunPE} have pointed out the
limitations and flaws of the Fisher Information Matrix, there has been
relatively few studies which investigate the BNS parameter estimation capabilities
of Advanced LIGO/Virgo using the techniques that will eventually be
employed.  The recent work of \cite{Vallisneri} and our own work
\citep{Inadequacies} has demonstrated that the Fisher matrix cannot
even be treated as a lower bound on the standard deviations of certain
parameters (particularly the masses) measurable in gravitational-wave
detectors.  While previous studies have employed MCMC techniques for specific
parameters,  \citep{Nissanke2011,Nissanke2013,Veitch2012}, none have considered 
the full range of parameters measurable for an optimal detection candidate.

In this paper, we perform a systematic study of the statistical
uncertainties with which the Advanced LIGO/Virgo network will be able
to measure the basic parameters of BNS mergers.  In Section
\ref{PEsection}, we describe the machinery of our parameter estimation
code, \texttt{LALInference}, and the associated MCMC sampler,
\texttt{lalinference\_mcmc}, as well as the frequency-domain
gravitational-wave template we employ.  In Section
\ref{resultsSection}, we qualitatively analyze the posterior
probability density functions for BNS systems with different masses
and extrinsic parameters.  We select three equal-mass and one unequal-mass
 binary systems as prototypical examples of BNS systems.  Each system is analyzed 40 
 times with isotropically selected sky locations and orbital orientations, and with a distance
 such that each signal was injected with a network signal-to-noise ratio of 20.
  The results are divided into three subsections of interest: the recovery of the mass
parameters (Section \ref{massSection}), the recovery of the orbital
inclination and luminosity distance (Section \ref{idSection}), and the
localization of sources on the sky (Section \ref{skySection}).
Finally we provide quantitative 1-dimensional credible intervals on
each parameter in Section \ref{ciSection}.  These results, contained
in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are
intended as a reference for the optimal BNS parameter estimation
capabilities of Advanced LIGO/Virgo.  We assume that $G=c=1$
throughout.

@@

We define the signal-to-noise ratio (SNR) of a gravitational wave in a
single detector as
\begin{equation}
  \rho \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{|
    \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df,
  \label{formalSNR}
\end{equation}
where $\rho$ is the SNR and $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
the frequency-domain data and template, respectively, and the
normalization $\sigma$ is given by
\begin{equation}
  \sigma^2 = 4\int^{\infty}_{0}\frac{| \tilde{h}(f)|^2}{S_n(f)}df.
  \label{SNRnorm}
\end{equation}

@@

\begin{equation}
\rho_{\text{network}} = \sqrt{\sum_i \rho_{i}^2}
\label{SNRnetwork}
\end{equation}

\noindent where $\rho_i$ is the SNR, given by \eqref{formalSNR}, of
the $i^{\text{th}}$ detector.

For this study, we consider four separate populations of BNS systems,
with component mass combinations of $1M_{\odot}/1M_{\odot}$,
$1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, and
$2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals
distributed randomly in sky location, polarization, inclination,
time-of-arrival, and coalescence phase.  The luminosity distance, $D$,
was selected to provide a network SNR of $\rho_{\text{network}}=20$
for each source in each network configuration. 
 While unphysical from an astrophysics perspective
(binary sources are expected to be distributed uniformly in co-moving volume), this
choice allows us to explore the parameter estimation in the context of
loud but plausible detection candidates.

Finally, note that the PSD that defines the inner
product \eqref{innerProduct} is simply the time-averaged sensitivity
of a given detector to a specific frequency.  Ignoring non-Gaussian
glitches, any stretch of data should contain a specific noise
realization drawn from a Gaussian colored by the PSD.  Without a
realistic model including the actual instrument sensitivity, non-stationary
 noise, and uncertainty in the PSD we cannot accurately
simulate gravitational-wave data to the point of making precise predictions about
parameter estimation capabilities.  Furthermore, the posterior
distribution from a future detection will be influenced by the
realization of the noise at the time of the detection.  Because of
this, we elect to focus only on the statistical errors due to the
flexibility of the waveforms and the expected sensitivity of the
advanced era detectors and suppress any effects of detector noise by
picking $n(t) \equiv 0$.  It can be shown that this ``zero-noise'' injection
represents the geometric mean of the same experiment over many different
noise realizations drawn from the same PSD.  See \cite{Nissanke2010}, c.f. equation
(53), for a proof that the geometric mean of the posteriors over many realizations of the 
noise is identical to the $n(t) = 0$ selection, given a sufficiently loud gravitational-wave
event.

Consequently, what we recover with the MCMC could be interpreted as
the posterior distribution function for each source averaged over all
possible (Gaussian) noise realizations, assuming we have the correct
PSD and that the signal is sufficiently powerful for the linearized-signal
approximation to be valid\footnote{This can also be seen in \cite{Vallisneri}, equation (74).
  By expanding the posterior variance as a series in $1/\text{SNR}$, it can be seen that the 
  $n(t) = 0$ posterior variance is identical to the frequentist average 
  over noise realizations of the posterior variance up to third order in $1/\text{SNR}$. }.
    By selecting a source population with an artificial distribution in SNR, we ensure that the
     ``zero-noise'' as average uncertainty approximation is valid.

To check that our reported statistical errors are not in gross
disagreement with those obtained in the presence of noise, we selected
a particular simulated signal to perform parameter estimation in
several noise realizations.  The comparison of the noise-dependent and
noise-free results can be found in Section \ref{noiseSection}.

@@

Unlike the mass parameters, the recovery of the position on the sky is
highly dependent on the location of the source with respect to the
detector network in question.  Much of the information about the sky
position of the source comes from the relative timing of the signals
in each detector.  For the HLV configuration, timing in the
three-detector network can only localize signals to one of two points
in the sky.  That is, when using only time-of-arrival information,
there is equal support in the probability density functions near true
location and near the point reflected through the plane formed by the
three detectors.  See \cite{Fairhurst2011} for a global analysis of
time-of-arrival accuracy for various network configurations, including
those considered here.

@@

Previous studies have considered the increase in sensitivity from the addition of the 
LIGO India site.  \cite{Nissanke2013} studied the decrease in
sky-location uncertainties obtained by the inclusion of the LIGO India site
into the advanced detector network.  Their study also employed an MCMC sampling technique 
 (a modified version of CosmoMC),
to determine the average parameter estimation uncertainties for a realistic distribution
of sources.  As the current study is interested in the uncertainties
of optimal sources at $\text{SNR}_{network}=20$, ignoring the effects of less viable 
detection candidates, it is instructive to compare the $95\%$ credible intervals
between the two studies.  The cumulative distributions of sky-area uncertainties
for both network configurations in each study are plotted in Fig. \ref{compSky}.

The difference in uncertainties between the two studies is illustrative.  \cite{Nissanke2013}
considered a realistic distribution of sources motivated by a local galaxy catalogue for
 sources where $D\leq 200\text{Mpc}$, and homogeneously distributed in co-moving
 volume for sources where $D > 200\text{Mpc}$.  These were then limited to those signals
 where $\text{SNR}_{network} \geq 8.5$ (the threshold for detection candidates in the
 current LIGO/Virgo software framework) for the MCMC parameter estimation.
   The current study considers a source
 population isotropically distributed on the sky, but at distances such that each signal
 represents an optimal case for parameter estimation.   Fig. \ref{compSky} compares
 the sky-area uncertainties that will be available to those considering ``good 
 gravitational-wave events'' (e.g. precision source isolation), and the 
 uncertainties that one can gather by considering all gravitational-wave candidates with 
 $\text{SNR}_{network}\geq 8.5$ (e.g. electromagnetic follow-up).  As expected, both source
 populations show a dramatic decrease in parameter estimation uncertainties with the
 addition of the LIGO India site to the advanced detector network.  This holds true even when
 considering the increased number of nominal sources available to the HLVI network 
 configuration in the Nissanke population, where the extension of the network detection 
 horizon due to the Indian detector increases the number of sources to 130, versus 90 in 
 the HLV configuration.

@@

 \caption{The cumulative fraction of sources found within $deg^2$ at the 95\% credible
 interval.  This plot contains results from two separate studies: the current study, in
 which optimal detection candidates are considered ($\rho_{network}=20$), 
and \cite{Nissanke2013}, which employs a separate MCMC code on a
 realistic source population (where $\rho_{trigger} \geq 8.5$ is employed to determine
 parameter estimation sources).  The optimal detection candidates are constrained
 to substantially smaller solid angles on the sky, as is expected for such ``gold-plated''
 events, while both studies show a substantial decrease in sky-area uncertainties for the HLVI configuration.}
 \label{compSky}
\end{figure}

@@

\begin{figure}[ht!]
  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
    clip=true,scale=0.52]{noisePDF.pdf}
 \caption{The effects of a non-zero noise realization on the recovered
   PDF for five different Gaussian realizations of the Advanced LIGO
   noise curve.  Each blue-dashed PDF represents the recovery of the same
   $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked
   at random from the Gaussian colored noise defined by the Advanced
   LIGO power spectral density, while the gray-shaded curve is the
   zero-noise PDF.  Notice how each curve is a Gaussian PDF with roughly similar shape,
   but different mean, to the zero-noise PDF.  This
   only holds true for glitch-free data, which is an unrealistic
   idealization when compared to real data.}
 \label{noisePDFs}
\end{figure}

We have performed the current analysis on zero-noise injections for
two reasons.  First, the results of a zero-noise analysis are
similar to those that would be achieved by averaging the results of
multiple identical injections in different Gaussian noise
realizations, as was argued in Section \ref{detectorSection}.  The second reason 
is we are not able
to predict the characteristics of realistic (often non-Gaussian)
advanced detector noise.  Attempting to do so would have little chance
of being accurate while requiring a huge computational burden to
combine the results of many MCMC runs in many different noise realizations.

In the case of a unique Gaussian realization of the Advanced LIGO
noise curve, each realization causes the maximum likelihood of the
posterior probability distribution to be translated away from the true
value.  These displacements tend to cancel 
    over many runs, ensuring that the mean uncertainties should be nearly identical to 
   the uncertainty drawn from the zero-noise runs.  Again, this only holds in the case
  where a signal is sufficiently loud that the posterior is linear in the parameters 
  $\thpara$.  Meanwhile, the posterior variances, averaged over many noise realizations, 
  are identical to the $n(t) = 0$ variance, up to third order in $1/\text{SNR}$.

@@

Of course, the largest concern for gravitational-wave parameter
estimation will not be the specific realization of Gaussian noise, but
the effects of non-Gaussianities in the data.  Techniques which build
off of the theoretical progress made
in~\cite{Allen:2002jw,Rover:2011qd,Littenberg:2010gf} for including
glitches in our model for the data, and therefore relaxing the
assumptions about stationary and Gaussian noise, are currently under
investigation.

@@

Finally, we reported the ability of advanced networks to constrain the
sky location of BNS signals.  It was found that the three-detector
configuration, consisting of the Washington and Louisiana LIGO sites
plus the Italian Virgo site, was able to constrain all signals within
64 $\mathrm{deg}^2$ (136 $\mathrm{deg}^2$) on the sky at the 68\% (95\%) 
credible level, with
an average median 68\% (95\%) credible interval of 
$4.6$ $\mathrm{deg}^2$ (12.2 $\mathrm{deg}^2$).
Meanwhile, the four-detector configuration, consisting of the
three-detector sites plus a LIGO India detector, was able to localize
all the sky locations to within 14 $\mathrm{deg}^2$ (45 $\mathrm{deg}^2$) on the sky at the 68\% (95\%)
credible interval, with an average median 68\% (95\%) credible interval of 
2 $\mathrm{deg}^2$ $(5.3$ $\mathrm{deg}^2)$.

@@

>>>>

Within the next few years, the first generation of gravitational-wave
interferometers capable of regularly detecting astrophysical sources will
come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Advanced Virgo
detectors (and the anticipated LIGO India detector)
 will provide the first insights into the final moments of
 compact object mergers, including the mergers of binary neutron
star systems.  Intense preparations are underway to characterize and
extract as much physical information as possible from these signals.

@@

By employing the full parameter-estimation machinery that will
eventually be used in the Advanced LIGO/Virgo era, our results
 give realistic estimates of the capabilities of
advanced ground-based detectors to characterize BNS systems.  Until
recently, the majority of studies have employed the Fisher-matrix
formalism which was first adapted for gravitational-wave parameter
estimation by \citet{FinnDetection}.  While each of these studies
\citep{PoissonWill,CutlerFlanagan,ArunPE} have pointed out the
limitations and flaws of the Fisher Information Matrix, there has been
relatively few studies which investigate the BNS parameter estimation capabilities
of Advanced LIGO/Virgo using the techniques that will eventually be
employed.  The recent work of \cite{Vallisneri} and our own work
\citep{Inadequacies} has demonstrated that the Fisher matrix cannot
even be treated as a lower bound on the standard deviations of certain
parameters (particularly the masses) measurable in gravitational-wave
detectors.  While previous studies have employed MCMC techniques for specific
parameters,  \citep{Nissanke2011,Nissanke2013,Veitch2012}, none have considered 
the full range of parameters measurable for an optimal detection candidates.

In this paper, we perform a systematic study of the statistical
uncertainties with which the Advanced LIGO/Virgo network will be able
to measure the basic parameters of BNS mergers.  In Section
\ref{PEsection}, we describe the machinery of our parameter estimation
code, \texttt{LALInference}, and its associated MCMC sampler,
\texttt{lalinference\_mcmc}, as well as the frequency-domain
gravitational-wave template we employ.  In Section
\ref{resultsSection}, we qualitatively analyze the posterior
probability density functions for BNS systems with different masses
and extrinsic parameters.  We select three equal-mass and one unequal-mass
 binary systems as prototypical examples of BNS systems.  Each system is analyzed 40 
 times with isotropically selected sky locations and orbital orientations, and with a distance
 such that each signal was injected with a network signal-to-noise ratio of 20.
  The results are divided into three subsections of interest: the recovery of the mass
parameters (Section \ref{massSection}), the recovery of the orbital
inclination and luminosity distance (Section \ref{idSection}), and the
localization of sources on the sky (Section \ref{skySection}).
Finally we provide quantitative 1-dimensional credible intervals on
each parameter in Section \ref{ciSection}.  These results, contained
in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are
intended as a reference for the optimal BNS parameter estimation
capabilities of Advanced LIGO/Virgo.  We assume that $G=c=1$
throughout.

@@

We define the signal-to-noise ratio (SNR) of a gravitational wave in a
single detector as
\begin{equation}
  \text{SNR} \equiv \frac{4}{\sigma} \int^{\infty}_{0}\frac{|
    \tilde{s}(f)\tilde{h}(f)|}{S_{n}(f)}df,
  \label{formalSNR}
\end{equation}
where $\tilde s(f)$ and $\tilde{h}^{*}(f)$ are
the frequency-domain data and template, respectively, and the
normalization $\sigma$ is given by
\begin{equation}
  \sigma^2 = 4\int^{\infty}_{0}\frac{| \tilde{h}(f)|^2}{S_n(f)}df.
  \label{SNRnorm}
\end{equation}

@@

\begin{equation}
\text{SNR}_{\text{network}} = \sqrt{\sum_i \text{SNR}_{i}^2}
\label{SNRnetwork}
\end{equation}

\noindent where $\text{SNR}_i$ is the SNR, given by \eqref{formalSNR}, of
the $i^{\text{th}}$ detector.

For this study, we consider four separate populations of BNS systems,
with component mass combinations of $1M_{\odot}/1M_{\odot}$,
$1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, and
$2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals
distributed randomly in sky location, polarization, inclination,
time-of-arrival, and coalescence phase.  The luminosity distance, $D$,
was selected to yield a signal strength of $\text{SNR}_{network}=20$
for each source in each network configuration. 
 While unphysical from an astrophysics perspective
(binary sources are expected to be distributed uniformly in co-moving volume), this
choice allows us to explore the parameter estimation in the context of
loud but plausible detection candidates.

Finally, note that the PSD that defines the inner
product \eqref{innerProduct} is simply the time-averaged sensitivity
of a given detector to a specific frequency.  Ignoring non-Gaussian
glitches, any stretch of data should contain a specific noise
realization drawn from a Gaussian colored by the PSD.  Without a
realistic model including the actual instrument sensitivity, non-stationary
 noise, and uncertainty in the PSD we cannot accurately
simulate gravitational-wave data to the point of making precise predictions about
parameter estimation capabilities.  Furthermore, the posterior
distribution from a future detection will be influenced by the
realization of the noise at the time of the detection.  Because of
this, we elect to focus only on the statistical errors due to the
flexibility of the waveforms and the expected sensitivity of the
advanced era detectors and suppress any effects of detector noise by
picking $n(t) \equiv 0$.  It can be shown \cite{Nissanke2010} that this ``zero-noise'' injection
represents the geometric mean of the same experiment over many different
noise realizations drawn from the same PSD.

Consequently, what we recover with the MCMC could be interpreted as
the posterior distribution function for each source averaged over all
possible (Gaussian) noise realizations, assuming we have the correct
PSD and that the signal is sufficiently powerful for the linearized-signal
approximation to be valid.  By selecting a source population with an
 artificial distribution in SNR, we ensure that the
     ``zero-noise'' as average uncertainty approximation is valid.  To check that our
      reported statistical errors are not in gross
disagreement with those obtained in the presence of noise, we selected
a particular simulated signal to perform parameter estimation in
several noise realizations.  The comparison of the noise-dependent and
noise-free results can be found in Section \ref{noiseSection}.

@@

Unlike the mass parameters, the recovery of the position on the sky is
highly dependent on the location of the source with respect to the
detector network in question.  Much of the information about the sky
position of the source comes from the relative timing of the signals
in each detector.  For the HLV configuration, timing in the
three-detector network can only localize signals to one of two points
in the sky.  That is, when using only time-of-arrival information,
there is equal support in the probability density functions near true
location and near the point reflected through the plane formed by the
three detectors.  See \cite{Fairhurst2011} for a global analysis of
time-of-arrival accuracy for various network configurations, including
those considered here.  See also \cite{Prospects2013} for a similar analysis,
applied to each stage of the advanced detector network.

@@

Previous studies have considered the increase in sensitivity from the addition of the 
LIGO India site.  \cite{Nissanke2013} studied the decrease in
sky-location uncertainties obtained by the inclusion of the LIGO India site
into the advanced detector network.  Their study also employed an MCMC sampling technique 
 (a modified version of CosmoMC),
to determine the average parameter estimation uncertainties for a realistic distribution
of sources.  As the current study is interested in the uncertainties
of optimal sources at $\text{SNR}_{network}=20$, ignoring the effects of less viable 
detection candidates, it is useful to compare the $95\%$ credible intervals
between the two studies.  The cumulative distributions of sky-area uncertainties
for both network configurations in each study are plotted in Fig. \ref{compSky}.

The difference in uncertainties between the two studies is illustrative.  \cite{Nissanke2013}
considered a realistic distribution of sources motivated by a local galaxy catalogue for
 sources where $D\leq 200\text{Mpc}$, and homogeneously distributed in co-moving
 volume for sources where $D > 200\text{Mpc}$.  These were then limited to those signals
 where $\text{SNR}_{network} \geq 8.5$ (the threshold for detection candidates in the
 current LIGO/Virgo matched-filtering framework) for the MCMC parameter estimation.
   The current study considers a source
 population isotropically distributed on the sky, but at distances such that each signal
 represents an optimal case for parameter estimation.   Fig. \ref{compSky} compares
 the sky-area uncertainties that will be available to those considering ``good 
 gravitational-wave events'' (e.g. precision source localization), and the 
 uncertainties that one can gather by considering all gravitational-wave candidates with 
 $\text{SNR}_{network}\geq 8.5$ (e.g. electromagnetic follow-up).  As expected, both source
 populations show a dramatic decrease in parameter estimation uncertainties with the
 addition of the LIGO India site to the advanced detector network.  This holds true even when
 considering the increased number of nominal sources available to the HLVI network 
 configuration in the Nissanke population, where the expansion of the network detection 
 horizon due to LIGO India increases the number of sources to 130, versus 90 in 
 the HLV configuration.  This trend is similar to that observed in \cite{Veitch2012}, contrasting
 the originally proposed four-detector configuration (with two co-located Hanford detectors) to 
 the HLVI configuration.

@@

 \caption{The cumulative fraction of sources found within $deg^2$ at the 95\% credible
 interval.  This plot contains results from two separate studies: the current study, in
 which optimal detection candidates are considered ($\text{SNR}_{network}=20$), 
and \cite{Nissanke2013}, which employs a separate MCMC code on a
 realistic source population (where $\text{SNR}_{trigger} \geq 8.5$ is employed to determine
 parameter estimation sources).  The optimal detection candidates are constrained
 to substantially smaller solid angles on the sky, as is expected for such ``gold-plated''
 events, while both studies show a substantial decrease in sky-area uncertainties for the HLVI configuration.}
 \label{compSky}
\end{figure}

@@

\begin{figure}[ht!]
  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
    clip=true,scale=0.52]{noisePDF.pdf}
 \caption{The effects of a non-zero noise realization on the recovered
   PDF for five different Gaussian realizations of the Advanced LIGO
   noise curve.  Each blue-dashed PDF represents the recovery of the same
   $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked
   at random from the Gaussian colored noise defined by the Advanced
   LIGO power spectral density, while the gray-shaded curve is the
   zero-noise PDF.  Notice how each curve is a Gaussian PDF with different mean and slightly
   different width
   , to the zero-noise PDF.  This
   only holds true for glitch-free data, which is an unrealistic
   idealization when compared to real data.}
 \label{noisePDFs}
\end{figure}

We have performed the current analysis on zero-noise injections for
two reasons.  First, the results of a zero-noise analysis are
similar to those that would be achieved by averaging the results of
multiple identical injections in different Gaussian noise
realizations.  For a unique Gaussian realization of the Advanced LIGO
noise curve, the realization causes the maximum likelihood of the
posterior probability distribution to be translated away from the true
value. These displacements tend cancel in the frequentist average over noise
 realizations, ensuring that the mean uncertainties should be nearly identical to 
   the uncertainty drawn from the zero-noise runs.  This can be seen in 
   \cite{Vallisneri}, equations (73) and (74).
  By expanding the posterior mean and the posterior variance as series in $1/\text{SNR}$,
   it can be seen that the 
  $n(t) = 0$ posterior mean is identical to the frequentist average 
  over noise realizations of the posterior mean to first order in $1/\text{SNR}$.  In similar
  fashion, the $n(t) = 0$ posterior variance is identical to the noise-realization frequentist 
  average up to third order in $1/\text{SNR}$.  As the current study operates in a high-SNR 
  regime, the zero-noise averages (particularly the averages of the posterior variances) are
   assumed to be valid.

@@

  Of course, this also relies on the assumption that the detector noise is Gaussian.  
  This is the second reason for employing the zero-noise approximation: it is not feasible
to predict the characteristics of realistic (i.e. non-Gaussian)
advanced detector noise.  Attempting to do so would have little chance
of being accurate while requiring a huge computational burden to
combine the results of many MCMC runs in many different noise realizations.
These non-Gaussian excursions will be one of the largest hurdles for parameter estimation
in the advanced detector era.
  Techniques which build
off of the theoretical progress made
in~\cite{Allen:2002jw,Rover:2011qd,Littenberg:2010gf} for including
glitches in the model for the data, and therefore relaxing the
assumptions about stationary and Gaussian noise, are currently under
investigation.

@@

Finally, we reported the ability of advanced networks to constrain the
sky location of BNS signals.  It was found that the three-detector
configuration, consisting of the Washington and Louisiana LIGO sites
plus the Italian Virgo site, was able to constrain all signals within
64 $\mathrm{deg}^2$ (136 $\mathrm{deg}^2$) on the sky at the 68\% (95\%) 
credible level, with
an average median 68\% (95\%) credible interval of 
$4.6$ $\mathrm{deg}^2$ (12.2 $\mathrm{deg}^2$).
Meanwhile, the four-detector configuration, consisting of the
three-detector sites plus a LIGO India detector, was able to localize
all the sky locations to within 14 $\mathrm{deg}^2$ (45 $\mathrm{deg}^2$) on the sky at the 68\% (95\%)
credible interval, with an average median 68\% (95\%) credible interval of 
2 $\mathrm{deg}^2$ $(5.3$ $\mathrm{deg}^2)$.  These high-SNR results
were then compared to similar results for a realistic, non-optimal source distribution from
\cite{Nissanke2013}.

@@

\section{Acknowledgements}

The authors would like to thank Samaya Nissanke, John Veitch, and Neil Cornish for useful discussions.  We would also like to thank Samaya Nissanke for the 95\% credible regions
quoted in Fig. \ref{compSky}. CR and BF were supported by NSF GRFP Fellowships, award DGE-0824162.
